---
title: "clean_data"
author: "Shachar oron "
date: "2023-11-20"
output: pdf_document
---
In this code i will try to clean and analyze the data of pd patiens (ON & OFF) and healthy patiens. 

```{r}
knitr::opts_knit$set(root.dir = 'C:/Users/shach/master/Master/data')

# Assuming your original data is stored in a variable named 'data'
data <- read.csv("../data/EC02_NB325/STRAIGHT_BASELINE/exports/000/gaze_positions.csv")

# Extract column names
column_names <- colnames(data)

# Print or view the column names
print(column_names)

```
Now i would like to clean the data , I have dicided that rows that has less than 0.5 in the "confidence" column, i will delete them. There will be still some NA values in the data, so, i installed the 'mice' library that replace the NA values with other values according to the distribution of the other values in the data. 
```{r}
knitr::opts_knit$set(root.dir = 'C:/Users/shach/master/Master/data')

# Remove rows with confidence less than 0.5
data <- data[data$confidence >= 0.5, , drop = FALSE]

# Load the 'mice' library
library(mice)

# Perform mice imputation
imputed_data <- mice(data, method = "pmm", m = 5)  # You can choose a different imputation method

# Extract the completed data
completed_data <- complete(imputed_data)

```
Remove rows with NA values:

```{r}
# Step 1: Remove Rows with Low Confidence
data <- data[data$confidence >= 0.5, , drop = FALSE]

# Step 2: Impute Missing Values Using 'mice'
# Install and load 'mice' library if not installed
#install.packages("mice")
library(mice)

# Replace "n" values with NA
data[data == "n" | data == "N"] <- NA

# Convert columns to numeric
data <- as.data.frame(lapply(data, as.numeric))

# Perform single imputation using mice
imputation_object <- mice(data, m = 1)

# Access the imputed data without modifying column names
imputed_data <- complete(imputation_object, action = "long", include = FALSE)

```

```{r}
# Specify the full path for saving the CSV file
output_file_path <- "../data/EC02_NB325/STRAIGHT_BASELINE/exports/000/imputed_data.csv"

# Save imputed data to a CSV file
write.csv(imputed_data, output_file_path, row.names = FALSE)

```
Now when we got our data cleaned. We will jump in and start by loading the clean data and analyze it. 





```{r}

knitr::opts_knit$set(root.dir = 'C:/Users/shach/master/Master/data')

# Function to clean and impute data for specific columns
clean_and_impute <- function(file_path) {
  # Read the data
  data <- read.csv(file_path)
  
  # Columns to impute
  columns_to_impute <- c("norm_pos_x", "norm_pos_y", "gaze_normal0_x", "gaze_normal0_y", "gaze_normal0_z",
                         "gaze_normal1_x", "gaze_normal1_y", "gaze_normal1_z")
  
  # Remove rows with confidence less than 0.5
  data <- data[data$confidence >= 0.5, , drop = FALSE]
  
  # Install and load 'mice' library if not installed
  # install.packages("mice")
  library(mice)
  
  # Replace "n" values with NA only in the specified columns
  data[, columns_to_impute][data[, columns_to_impute] == "n" | data[, columns_to_impute] == "N"] <- NA
  
  # Convert columns to numeric
  data[, columns_to_impute] <- lapply(data[, columns_to_impute], as.numeric)
  
  # Perform single imputation using mice only for specified columns
  imputation_object <- mice(data[, columns_to_impute], m = 1)
  
  # Access the imputed data without modifying column names
  imputed_data <- complete(imputation_object, action = "long", include = FALSE)
  
  # Merge the imputed data with the original data
  data_imputed <- merge(data, imputed_data, by = 0, all.x = TRUE)
  
  # Specify the output file path
  output_file_path <- file.path(dirname(file_path), "imputed_data.csv")
  
  # Save imputed data to a CSV file
  write.csv(data_imputed, output_file_path, row.names = FALSE)
}

# Find all files named "gaze_positions.csv" under "../data"
files <- list.files(path = "../data", pattern = "gaze_positions.csv", recursive = TRUE, full.names = TRUE)

# Apply the clean_and_impute function to each file
lapply(files, clean_and_impute)


```


